Map/Reduce for the common man

### 2010-02-17 doc/slides.tex
*** empty log message ***

\begin{frame}\frametitle{Google's Map/Reduce}
  what it is

  what it offers

  application domains

\end{frame}

@@

@@

\begin{frame}\frametitle{Future Work}

\end{frame}

@@

>>>>

\begin{frame}\frametitle{Google's Map/Reduce}
  \begin{itemize}
  \item 
    what it is
    \begin{itemize}
    \item a paradigm for distributed computing at Google
    \end{itemize}

    \bigskip
  \item 
    what it offers
    \begin{itemize}
    \item abstraction to hide parallelization and distribution from
      user level code
    \end{itemize}

    \bigskip
  \item 
    application domains
    \begin{itemize}
    \item large scale data processing
    \end{itemize}
  \end{itemize}

  \vfill
  [MapReduce: Simplified Data Processing on Large Clusters. \par
  J. Dean and S. Ghemawat. OSDI 2004]
\end{frame}

\begin{frame}\frametitle{Main Idea}
  the user provides two functions
  \begin{itemize}
  \item \emph{map}: takes a key/value pair and returns a list of key/value
    pairs
    \begin{ocaml}
    map : k1 * v1 -> (k2 * v2) list
    \end{ocaml}

  \item \emph{reduce}: takes a list of values for one key and returns
    another list for that key
    \begin{ocaml}
    reduce : k2 * v2 list -> v2 list
    \end{ocaml}
  \end{itemize}

  and the library takes care of the rest
\end{frame}

\begin{frame}\frametitle{}
  \begin{center}
    \includegraphics[width=\textwidth]{mrwordcount}
  \end{center}
\end{frame}

\begin{frame}\frametitle{}
  \begin{center}
    \includegraphics[width=\textwidth]{mrfigure}
  \end{center}
\end{frame}

@@

\begin{frame}\frametitle{Ocaml's Map/Reduce}
  \begin{itemize}
  \item 
    what it is
    \begin{itemize}
    \item a distributed computing library for Ocaml users
    \end{itemize}

    \bigskip
  \item 
    what it offers
    \begin{itemize}
    \item abstraction to hide parallelization and distribution from
      user level code
    \item \emph{polymorphism}
    \item \emph{multi-cores or clusters}
    \end{itemize}

    \bigskip
  \item 
    application domains
    \begin{itemize}
    \item large scale data processing
    \item \emph{and much more}
    \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{Future Work}
  \begin{itemize}
  \item fault tolerance
    \begin{itemize}
    \item blacklist faulty workers
    \item ping workers periodically
    \end{itemize}
  \item use idle workers to speedup remaining tasks
  \end{itemize}
\end{frame}

@@

% LocalWords:  parallelization Google
